% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt

\usepackage{url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}

% hyperref package for links
\usepackage[pdfborder={0 0 0}]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Tiago Luchini}                  % name for signature
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{Ms. Jessica Apelowicz \\
Kira Systems}


\begin{flushleft}
{\large\bf Tiago Luchini}
\end{flushleft}
\medskip\hrule
\begin{flushright}
\hfill 10 City Point, Apt. 27G, Brooklyn, NY 11201 (Green card holder)\\ \hfill
\href{mailto:tiago@luchini.nyc}{tiago@luchini.nyc} ~~
\href{https://luchini.nyc}{https://luchini.nyc} ~~ \href{tel:+16466847728}{+1
  (646) 684 7728}
\end{flushright}
\vfill % forces letterhead to top of page
 
\opening{Dear Jessica,}

\noindent I am an accomplished Technology leader with an extensive
global career building and scaling Software Development businesses and
teams ranging from loss-making units to multi-million, multi-year,
multi-geography digital products.

\noindent Despite a long career in leadership roles I'm a practioner
at heart and have kept my skills sharpened not only by actively
engaging in the projects I led but also being prolific in the Open
Source community. My original OSS work is around data-intensive
applications, developer tools, DSLs, APIs, data-pipelines, distributed
systems, and resilient applications. More details can be found on
\href{https://luchini.nyc}{my website} but here's a summary:

\begin{itemize}
\item \href{https://github.com/luchiniatwork/hodur-engine}{Hodur}, a
  domain modeling approach and collection of libraries to Clojure. By
  using Hodur developers can define domain model as data, parse and
  validate it, and then either consume it via an API or use one of the
  plugins to help achieve mechanical results faster and in a purely
  functional manner.

\item \href{https://github.com/luchiniatwork/terra}{Terra} lets
  developers and DevOps engineers write Terraform configurations in
  pure Clojure by leveraging the power of Clojure macros. It extends
  the reach of infrastructure-by-code with Clojure.

\item \href{https://github.com/luchiniatwork/migrana}{Migrana} is a
  Datomic migration tool that gives developers control over how their
  schema evolves. By giving a temporal timeline of schema evolutive
  steps and letting developers tap into teshe steps, it offers a
  simple alternative to manual schema management.

\item \href{https://github.com/luchiniatwork/cambada}{Cambada}, a
  packager for Clojure based on deps.edn (AKA tools.deps). Supporting
  jar, uberjar, and - particularly - GraalVM’s native-image.

\item
  \href{https://github.com/luchiniatwork/resilience4clj-circuitbreaker}{Resilience4Clj}
  is a lightweight fault tolerance library set built on top of
  GitHub’s Resilience4j, inspired by Netflix Hystrix, and designed for
  Clojure and functional programming with composability in mind.

\end{itemize}

\noindent I'm also a keen public speaker around some of the subjects
that I'm passionate about. Here are the links to some of my latest
talks:

\begin{itemize}
  \item \href{https://www.youtube.com/watch?v=uL9QavmAInw}{The Power
    of Lacinia \& Hystrix in Production} at the Clojure/conj 2018
  \item \href{https://www.youtube.com/watch?v=EDojA_fahvM}{Declarative
    Domain Modeling for Datomic Ion/Cloud} at tge Clojure/conj 2017
\end{itemize}

\noindent It would be a pleasure to engage in a personal
interview. I’m pretty flexible as to the time and place. Feel free to
reach me by email or phone. Thank you for taking the time to consider
my credentials.

\closing{Sincerely yours,}


\end{letter}


\end{document}
