% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt

\usepackage{url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}

% hyperref package for links
\usepackage[pdfborder={0 0 0}]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=9in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Tiago Luchini}                  % name for signature
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{To Talent Acquisition Department,}


\begin{flushleft}
{\large\bf Tiago Luchini}
\end{flushleft}
\medskip\hrule
\begin{flushright}
\hfill 63 Hortontown Hill Rd., Hopewell Junction, NY 12533 (Green card holder)\\ \hfill
\href{mailto:tiago@luchini.nyc}{tiago@luchini.nyc} ~~
\href{https://luchini.nyc}{https://luchini.nyc} ~~ \href{tel:+16466847728}{+1
  (646) 684 7728}
\end{flushright}
\vfill % forces letterhead to top of page
 
\opening{}

\noindent My passion is to help organizations build digital products \&
the teams behind them. I enjoy socio-technological challenges, growing
teams across multiple countries \& spanning industries while managing a
diverse set of people, technologies \& processes.

\noindent During the last decades, I've built meaningful digital
products people use every day for numerous Fortune 500 companies, tech
startups \& non-profits on a wide range of innovative software \&
hardware projects ranging from short, one-month engagements to
multi-million, multi-year, multi-geography endeavors.

\noindent I appreciate opportunities to attract, mentor, and lead
great software engineers and to design engineering organizations that
thrive in a fulfilling culture.

\noindent Key highlights:

\begin{itemize}
\item 24 years of experience, 7 of which in senior leadership roles at
  startups as well as well-established engineering
  organizations. Experience in rapid team and business ramp
  up. Demonstrated experience in the 0 to 200+ person engineering
  organization range.

\item Passion for the people and the cultural side of engineering
  organizations. Experience scaling through hiring and effective
  organizational design.

\item Practitioner at heart having kept my skills sharpened by
  actively engaging in the projects I led but also being prolific in
  the Open Source community. Demonstrated passion for the craft of
  engineering.

\item Original OSS work around data-intensive applications, developer
  tools, DSLs, APIs, data-pipelines, distributed systems, and
  resilient applications.

\item Expertise in infrastructure, architecture, mobile
  development, site reliability engineering, and DevOps.

\item Experience working in highly collaborative organizations where
  Engineering, Product, Design, and Business functions work actively
  together. Passion for product excellence.

\end{itemize}


\noindent I'm also a keen public speaker and have talked on some of
the subjects I'm passionate about. Here are the links to some of my
latest talks:

\begin{itemize}
  \item \href{https://www.youtube.com/watch?v=KtN0vqOlmn8}{Building
    Resilient Apps} at Heart of Clojure 2019
  
  \item \href{https://www.youtube.com/watch?v=EDojA_fahvM}{Declarative
    Domain Modeling for Datomic Ion/Cloud} at the Clojure/conj 2018

  \item \href{https://www.youtube.com/watch?v=uL9QavmAInw}{The Power
    of Lacinia \& Hystrix in Production} at the Clojure/conj 2017
\end{itemize}

\noindent It would be a pleasure to engage in a personal
interview. I’m pretty flexible as to the time and place. Feel free to
reach me by email or phone. Thank you for taking the time to consider
my credentials.

\closing{Sincerely yours,}


\end{letter}


\end{document}
